% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Bhavik}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-1in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header  
\name{\Large \centerline{Bhavik Dhandhalya}\\ 
\centerline {bhavik.bitspilani@gmail.com}\\[12pt]}% the \\[12pt] adds a blank line after name

\address{{1117 CVR Bhawan} \\ BITS Pilani, Pilani Campus \\
  Rajasthan, IND \\ Pilani-333031}      
                                      
\address{{(+91) 942-787-3839} \\ h20180118@pilani.bits-pilani.ac.in \\
  https://github.com/BhavikDhandhalya}



\begin{resume}
 
\section{{\Large Education}} 
\vspace{8pt}

{\sc Birla Institute of Technology \& Science}, Pilani, IND \hfill Expected May 2020
\begin{itemize}
\item M.E. in Computer Science, GPA 0.00
\end{itemize}

{\sc Charusat University of Science \& Technology}, Changa, IND \hfill May 2017
\begin{itemize}
\item B.Tech. in Computer Engineering, GPA 7.06
\item Secured 3rd Rank in 8th Semester by scoring perfect 10.00.
\end{itemize}
  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.01in} 
\section{{\Large Professional Experience}} 
\vspace{8pt}

{\sc \underline{Charusat Space Research \& Technology Center}}, Changa, IND\\
{\it Research Intern} \hfill Jan 2017 -- Apr 2017
\begin{itemize}
\item Project Title: Non-rigid Image Registration on Videos distorted by Atmospheric Turbulence.
\item  Applied and Analyzed algorithms such as CGI(Control Grid Interpolation), Lucas - Kanade,
FRATAAS(First Register Then Average and Subtract) to remove Heat Scintillation.
\item Improvements were made on scene change and moving object recovery situations.
\item Proposed new method called ``Dual Registration'' to handle high Scintillations. [MATLAB]
\end{itemize}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.01in} 
\section{{\Large Honors}} 
\vspace{15pt}
\begin{itemize}
\item secured \underline{Rank 64th in ACM ICPC Asia Kolkata Regional 2016} after competing with 900+ teams in Online Round.
\item Contestant at \underline{ACM ICPC Asia Amritapuri Regional 2015} after competing with 1500+ teams in Online Round.
\item Secured All-India-Rank 491 among 1,07,893 candidates in GATE - Graduate Aptitude Test for Master Degree's Admission in India. Exam Stream : Computer Science.
\item Qualified for Semi-Final Round in TCS Codevita season 4 \& 5 Coding Competition.
\item Secured 38th Rank out of 800+ participants in CodeVaitam Coding Competition conducted by NIT Agartala on Codechef platform.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.01in} 
\section{{\Large Projects}} 
\vspace{8pt} % reduce space between section title and contents

{\sc Load Balancing on Software Defined Network(SDN)} | {\it Network} \hfill Aug 2018 -- Present
\begin{itemize}
\item Improving Round-Robin and Dynamic load balancing methods proposed in IEEE 2015 \& ICNNA 2016 respectively. [Mininet]
\end{itemize}

{\sc Zombie Hunt Game} | {\it Algorithm} \hfill Jan 2016 -- Apr 2016
\begin{itemize}
\item Created this game where each Zombie follows the player using the Shortest Path Finding Algorithm called A*(A-Start) Algorithm by calculating Heuristic Values.
\item Implemented weapon facilities to kill Zombies. [python 2.7, pygame]
\end{itemize}

{\sc File Transfer using Selective Repeat Protocol using UDP Packets} | {\it Network} \hfill Jan 2015 -- Apr 2015
\begin{itemize}
\item Implemented Multi-threading function at Sender \& Receiver side to Send \& Receive UDP Packets/ACKs.
\item Implemented Time-Out-Timer to resend lost packets. [C++, pthread]
\end{itemize}

{\sc Terminal Based Quiz using RPC} | {\it Operating System} \hfill Sep 2014 -- Nov 2014
\begin{itemize}
\item Using Remote Procedure Call, Client attempts Quiz consist of 50 Random Questions. Any number of clients can interect with Server simultaneously. Implemented Rank feature.
\item Handled unexpected failures by storing last status of Clients at Server side. [C]
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.01in} 
\section{{\Large Survey/Term Presentation}} 
\vspace{8pt}
 
{\sc Critical Analysis of Quorum based Distributed Mutual Exclusion Algorithms} | {\it Distributed Systems} \hfill Aug 2018 -- Present
\begin{itemize}
\item Comparing Algorithms based on various performance matrix such as the Order of messages for critical section invocation, synchronization and response time.
\end{itemize}

{\sc Monte Carlo Factorization Approximation Algorithm} | {\it Algorithm} \hfill Aug 2018 -- Present
\begin{itemize}
\item Presented survey of Monte Carlo Factorization Approximation Algorithm.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.01in} 
\section{{\Large Position of Responsibility}} 
\vspace{8pt}

\begin{itemize} \vspace{8pt}
\item Curated Algorithmic programming problems for ``Clash of Coders'' a national level online series at HackerEarth. \hfill Jan 2015 - Apr 2016
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.01in} 
\section{{\Large Extra Interests}} 
\vspace{8pt}

\begin{itemize} \vspace{8pt}
\item Solved 600+ algorithmic problems on various online programming platforms like Codeforces, Codechef, HackerRank.
\end{itemize}


 
\end{resume} 
\end{document}













